---
name: Jesse Mbaria
surname: Mwangi
#position: "Mr"
#pronouns: He/Him
profilepic: jay.jpg
address: "Thika, 3917-01002"
phone: 703705137
www: jeseembariah.com
email: "jessebaryah@gmail.com"
twitter: jaymbaria
github: jaymbaria
linkedin: Jay
aboutme: "A disciplined, Adaptable and motivated leather science and technology graduate, intending to continue personal development as a leather technologist. I think in terms of results and objectives. I am enthusiastic, and I work with decisiveness and conviction. I have a proactive attitude and find positive ways to stimulate and engage with people."
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(purrr)

# install.packages("readxl") uncomment this if you need to install the package
library(readxl)
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  # import each sheet into a list using readxl::read_excel
  list <- map(all, function(x) readxl::read_excel(filename, sheet = x))
  # save sheet name for each sheet (list)
  names(list) <- all
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}


jay <- here::here("jay.xlsx")
readExcelSheets(jay)
```

# Research Project

Did a Research project to determine the nutritional value of the tannery green fleshing for potential use in Aqua feeds formulation thus reduction of tannery solid waste. Hence replacement of fish meal with proteinaceous tannery solid waste will be the best approach to ease out solid waste disposal problem for environmentalist and also beneficial as an economic feed in aquaculture.


# Education
```{r}
education %>% 
  detailed_entries(what = degree,
                   when = year,
                   with = institution,
                   where = where,
                   why = details)
```

# Work Experience

```{r}
industry |> 
  detailed_entries(what = institution,
                   when = dates,
                   with = role,
                   where = where,
                   why = details)
```

# Leadership

```{r}
leadership |> 
  detailed_entries(what = institution,
                   when = dates,
                   with = role,
                   where = where,
                   why = details)
```

# Skills
```{r}
skills |> 
  detailed_entries(with = skill)
```

# Referees
```{r}
library(tibble)
tribble(
  ~ Supervisor, ~ Department, ~ Institution, ~ Contact, ~Email,
  "Mr. Joel Mwondu", "Leather science and technology", "University of Nairobi)", "+254717186315","Joelmwondu@uonbi.ac.ke",
  "Mr. Dennis Kimaiga", "KALTS", "The Kenya Association of Leather Technologist and Scientist (KALTS)", " +254715431073"," dkimaiga@uonbi.ac.ke") %>%
  detailed_entries(what = Institution, 
                   where = Department, 
                   with = Supervisor, 
                   when = Contact, 
                   why =Email)
```

